Increasing Performance via Gamification in a Volunteer-Based Evolutionary Computation System

### 2018-01-09 2018-IPMU/Gamification/paper.tex
@jj please check the figure
Single Figure 1 as requested in issue #10.

\begin{figure}[h!tb]
    \centering
        \includegraphics[width=0.9\linewidth]{img/puts_user.png}
        \includegraphics[width=0.9\linewidth]{img/puts_ip.png}
    \caption{Usage by registered (top) and anonymous (bottom) users.  Users are ranked by
        the number of requests sent, in the \emph{x} axis is the rank, and in the \emph{y} axis
        number or PUTs in a logarithmic scale.}
      \label{fig:puts}
% Maybe we should scale dividing by number of users and put them
% together. - JJ
\end{figure}
%
Contributions are counted by the number of HTTP {\tt PUT} requests
sent to the server. In Figure~\ref{fig:puts} a comparison between the 
contribution of registered vs anonymous users is presented.

>>>>

\begin{figure}[h!tb]
    \centering
        \includegraphics[width=0.9\linewidth]{img/puts.png}

    \caption{Usage by registered (green triangles) and anonymous (red dots) users.  Users are ranked by
        the number of requests sent, in the \emph{x} axis is the rank, and in the \emph{y} axis
        number of PUTs in a logarithmic scale.}
      \label{fig:puts}
% Maybe we should scale dividing by number of users and put them
% together. - JJ
\end{figure}
%
Contributions are counted by the number of HTTP {\tt PUT} requests
sent to the server. In Figure~\ref{fig:puts} a comparison between the 
contribution of registered vs anonymous users is presented.
